### 2016-11-16 src/abstract.tex
intro

The \textsc{maximum carpool matching} problem is a star packing problem in
directed graphs.
Formally, given a directed graph $G = (V, E)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : E \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
and $M$ is a subset of $E \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{maximum carpool matching} 
problem we seek for a matching $(P, D, M)$ that maximizes the total weight of $M$.

>>>>

The \textsc{\CARPOOL{}} problem is a star packing problem in
directed graphs.
Formally, given a directed graph $G = (V, E)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : E \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
and $M$ is a subset of $E \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{\CARPOOL{}} 
problem we seek for a matching $(P, D, M)$ that maximizes the total weight of $M$.
